Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
slight rephrasing in the first paragraph of Section 4

Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial parameters and full ionization. This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.

@@

In this section, we discuss the observability of the estimated radio emission. 
An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult to identify the planetary contribution.
We will see in Section \ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
Then, we estimate the radio emission of Jupiter-twin around known M giants in Section \ref{ss:actualMgiants}. 
In Section \ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
radio instruments at relevant frequencies.
Finally, Section \ref{ss:timevariability} points out the polarization and the time variability of the radio emission as keys to discern the signals from the background noise.

>>>>

Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization. This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.

@@

In this section, we discuss the observability of the estimated radio emission. 
An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult to identify the planetary contribution.
We will see in Section \ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
Then, in Section \ref{ss:actualMgiants}, we estimate the radio flux from hypothetical Jupiter-like planets around known M giants. 
In Section \ref{ss:detectability}, we examine the sensitivities and limitations of several current and future
radio instruments at relevant frequencies.
Finally, Section \ref{ss:timevariability} points out the polarization and the time variability of the radio emission as keys to discern the signals from the background noise.
